Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-05 Tex/Old text/chapters/chapteroptimization.tex
thesis update

In this Chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking. Diagrams, flowcharts, and algorithms support and explain the solutions.

@@

Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} version 1.8 with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency. Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory. The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purposes.

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

>>>>

In this Chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking. Diagrams, flowcharts, and algorithm give support and explain the solutions.

@@

Three start-of-the-art verification tools, CBMC\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} version 5.11 with MiniSat 2.2.1~\cite{Kroening}, ESBMC\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} version 6.0.0 with the  Boolector 3.0.1 solver~\cite{Brummayer}, %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c} version 1.8 in a configuration as bound model checking and with MathSAT 5.5.3~\cite{mathsat5}, were used as verification engines to compare the proposed approach effectiveness and efficiency. Note that ``incremental'' ESBMC with the SMT solver Z3 version 4.7.1~\cite{DeMoura} was tried\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} as an alternative to use less computing memory. The Simulation tool HOMER Pro version $3.13.1$ was used for comparative purposes.

@@

\begin{table}
\caption{Case studies and results: optimization of stand-alone PV systems.}\label{tab1}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
Tools & \makecell{CBMC 5.11 \\(MiniSat 2.2.1)}& \makecell{ESBMC 6.0.0 \\(Boolector 3.0.1 /\\Z3 4.7.1)}& \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & OM & TO / IF & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} & OM & TO / IF & \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & OM & TO / IF & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Legend: OM = out of memory; TO = time out; IF = internal failure, E = energy.
\end{scriptsize}
\end{table}

### 2020-02-05 Tex/Old text/chapters/chapterverification.tex
thesis update

The verification engine CPAchecker 1.8 was used \footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}. An alternative CPAchecker configuration was also tried, using the BMC k-induction option, but the results show no improvement in performance or soundness (so it is not reported here).

@@

%HOMER Pro result: the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation. The simulation took less than five seconds to be performed on each case study.
%
\begin{table}
\centering
\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
\multicolumn{5}{c}{Model Checker (SAT/UNSAT: time and message)}\\
\hline
Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
\hline
\hline
House 1 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 08 s \\(UNSAT)} & \makecell{19 m 02 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
\hline
House 2 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 27 s \\(UNSAT)} & \makecell{18 m 59 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
\hline
House 3 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{05 m 07 s \\(UNSAT)} & \makecell{18 m 39 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
\hline
House 4 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{04 m 37 s \\(UNSAT)} & \makecell{18 m 36 s \\(UNSAT)} & \makecell{Time out \\ (UNKNOWN)}\\
\hline
House 5 &  \makecell{Out of memory \\(UNKNOWN)} & \makecell{$\leq$ 1 sec \\(SAT)} & \makecell{$\leq$ 1 sec \\(SAT)} & \makecell{6 sec \\ (SAT)}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}

>>>>

The verification engine CPAchecker 1.8 was used in a configuration of bound model checking\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -stack 10240k -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc -benchmark filename.c}, with the SMT solver MathSAT version 5.5.3~\cite{mathsat5}. An alternative CPAchecker configuration was also tried, using the BMC k-induction option, but the results show no improvement in performance or soundness (so it is not reported here).

@@

%HOMER Pro result: the $1,200$W was the only one that was proved to not meet the requirement of battery autonomy; all the 700W systems had no indication of flaws during simulation. The simulation took less than five seconds to be performed on each case study.
%
\begin{table}
\centering
\caption{Summary of the case-studies comparative and the automated tools.}\label{cases}
\begin{scriptsize}
\begin{tabular}{c|c|c|c|c}
\hline
\hline
\multicolumn{5}{c}{Model Checker (SAT/UNSAT: time, message, and used memory)}\\
\hline
Case &  \makecell{ESBMC 6.0.0\\(Boolector 3.0.1)} & \makecell {ESBMC 6.0.0\\(Z3 4.7.1)} & \makecell{CBMC 5.11\\(MiniSat 2.2.1)} & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}\\
\hline
\hline
House 1 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT) \\ 44 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.36 s \\ (SAT) \\ 173 MB}\\
\hline
House 2 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 44 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.34 s \\ (SAT)\\174 MB}\\
\hline
House 3 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 45 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.38 s \\ (SAT)\\ 174 MB}\\
\hline
House 4 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 45 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.46 s \\ (SAT)\\ 176 MB}\\
\hline
House 5 &  \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{$\leq$ 1 sec \\(SAT)\\ 45 MB} & \makecell{Out of memory \\(UNKNOWN)\\$\geq$ 64 GB} & \makecell{4.19 s \\ (SAT)\\ 174 MB}\\
\hline
\hline
\end{tabular}
\end{scriptsize}
\end{table}
